Manuscript

### 2018-12-06 manuscript.Rmd
g2p DGL stats, new summ plots

```{r}
library(bsselectR)
library(data.table)
library(ggpubr)
library(ggrepel)
library(ggsignif)
library(htmlwidgets)
library(kableExtra)
library(plotly)
library(reshape2)
library(scales)
library(tidyverse)
```

@@

g2p$Drug <- tolower(g2p$Drug)
g2p[g2p == -1] <- NA
g2p$Ref[g2p$Ref == "None"] <- NA
g2p$Alt[g2p$Alt == "None"] <- NA
g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))

g2p_drug_genes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))
g2p_drug_genes
g2p_genes
g2p_drugs
# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

@@

# CCLE
ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ccle <- merge(drug_meta, ccle, by = "CID")
ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "ActArea")
ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Wildtype", ccle_data$Mutation_Status_Nonsilent)
ccle_data <- merge(ccle_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
# ccle_data <- merge(ccle_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
ccle_data <- merge(ccle_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
ccle_data$ActArea <- as.numeric(ccle_data$ActArea)
# CCLE AUC is actually AOC
# assuming scale is 0-8, transform to range between 0 and 1
# get AUC by 1 - AOC
ccle_data$AUC <- 1 - (ccle_data$ActArea / 8)
ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
ccle_data$AUC_zscore <- (ccle_data$AUC - mean(ccle_data$AUC)) / sd(ccle_data$AUC)
ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Wildtype", "palegreen3", "springgreen4")
ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q4_g2pgenes.rds", compress = "xz")

# CTRP
ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ctrp <- merge(drug_meta, ctrp, by = "CID")
ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = g2p_genes)
ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Wildtype", ctrp_data$Mutation_Status_Nonsilent)
ctrp_data <- merge(ctrp_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
# ctrp_data <- merge(ctrp_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
ctrp_data <- merge(ctrp_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
ctrp_data$AUC_zscore <- (ctrp_data$AUC - mean(ctrp_data$AUC)) / sd(ctrp_data$AUC)
ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Wildtype", "slategray3", "steelblue4")
ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds", compress = "xz")

# GDSC
gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
gdsc <- merge(drug_meta, gdsc, by = "CID")
gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = g2p_genes)
gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Wildtype", gdsc_data$Mutation_Status_Nonsilent)
gdsc_data <- merge(gdsc_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
# gdsc_data <- merge(gdsc_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
gdsc_data <- merge(gdsc_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
gdsc_data$AUC_zscore <- (gdsc_data$AUC - mean(gdsc_data$AUC)) / sd(gdsc_data$AUC)
gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Wildtype", "paleturquoise3", "turquoise4")
gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds", compress = "xz")
```

@@

@@

```{r, eval=FALSE}
ccle_signif_g2p_lineage <- lapply(unique(ccle_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_grid, data_name = "ccle", grouping_var = "lineage")
names(ccle_signif_g2p_lineage) <- unique(ccle_signif_g2p_lineage$Drug)
ccle_signif_g2p_lineage <- rbindlist(ccle_signif_g2p_lineage, use.names = TRUE)
ccle_signif_g2p_lineage <- ccle_signif_g2p_lineage[order(ccle_signif_g2p_lineage$p),]
saveRDS(ccle_signif_g2p_lineage, "./data_munging/rds/ccle_signif_g2p_lineage.rds")
```

```{r}
ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
knitr::kable(ccle_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

knitr::kable(ccle_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r, eval=FALSE}
ctrp_signif_g2p_lineage <- lapply(unique(ctrp_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_grid, data_name = "ctrp", grouping_var = "lineage")
names(ctrp_signif_g2p_lineage) <- unique(ctrp_signif_g2p_lineage$Drug)
ctrp_signif_g2p_lineage <- rbindlist(ctrp_signif_g2p_lineage, use.names = TRUE)
ctrp_signif_g2p_lineage <- ctrp_signif_g2p_lineage[order(ctrp_signif_g2p_lineage$p),]
saveRDS(ctrp_signif_g2p_lineage, "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
```

```{r}
ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
knitr::kable(ctrp_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r, eval=FALSE}
gdsc_signif_g2p_lineage <- lapply(unique(gdsc_data_g2p_grid$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_grid, data_name = "gdsc", grouping_var = "lineage")
names(gdsc_signif_g2p_lineage) <- unique(gdsc_signif_g2p_lineage$Drug)
gdsc_signif_g2p_lineage <- rbindlist(gdsc_signif_g2p_lineage, use.names = TRUE)
gdsc_signif_g2p_lineage <- gdsc_signif_g2p_lineage[order(gdsc_signif_g2p_lineage$p),]
saveRDS(gdsc_signif_g2p_lineage, "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
```

```{r}
gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
knitr::kable(gdsc_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

## Drugscreen: G2P evidence

@@

crispr_mut_heatmap_plot <- ggplot(data = crispr_signif_g2p_gene, aes(x = Hugo_Symbol, y = y_label)) +
  geom_tile(aes(fill = p)) +
  scale_fill_gradientn(colors = c("darkgreen", "white", "white"), values = c(0, 0.05, 1), na.value = "darksalmon") +
  scale_x_discrete(drop = FALSE) +
  theme(axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
  labs(x = "Gene")

@@

>>>>

```{r}
library(bsselectR)
library(cowplot)
theme_set(theme_light())
library(data.table)
library(ggpubr)
library(ggrepel)
library(gridExtra)
library(ggsignif)
library(htmlwidgets)
library(kableExtra)
library(plotly)
library(reshape2)
library(scales)
library(tidyverse)
```

@@

g2p$Drug <- tolower(g2p$Drug)
g2p[g2p == -1] <- NA
g2p$Ref[g2p$Ref == "None"] <- NA
g2p$Alt[g2p$Alt == "None"] <- NA
g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))

g2p_druggenelins <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
g2p_drug_genes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))
g2p_drug_genes
g2p_genes
g2p_drugs
# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

@@

# CCLE
ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ccle <- merge(drug_meta, ccle, by = "CID")
ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "ActArea")
ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Wildtype", ccle_data$Mutation_Status_Nonsilent)
ccle_data <- merge(ccle_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
# ccle_data <- merge(ccle_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
ccle_data <- merge(ccle_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
ccle_data$ActArea <- as.numeric(ccle_data$ActArea)
# CCLE AUC is actually AOC
# assuming scale is 0-8, transform to range between 0 and 1
# get AUC by 1 - AOC
ccle_data$AUC <- 1 - (ccle_data$ActArea / 8)
ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
ccle_data$AUC_zscore <- (ccle_data$AUC - mean(ccle_data$AUC)) / sd(ccle_data$AUC)
ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Wildtype", "palegreen3", "springgreen4")
ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
ccle_data$Drug_Gene_Lin <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol, "_", ccle_data$group_general_lineage_name)
saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q4_g2pgenes.rds", compress = "xz")

# CTRP
ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ctrp <- merge(drug_meta, ctrp, by = "CID")
ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = g2p_genes)
ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Wildtype", ctrp_data$Mutation_Status_Nonsilent)
ctrp_data <- merge(ctrp_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
# ctrp_data <- merge(ctrp_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
ctrp_data <- merge(ctrp_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
ctrp_data$AUC_zscore <- (ctrp_data$AUC - mean(ctrp_data$AUC)) / sd(ctrp_data$AUC)
ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Wildtype", "slategray3", "steelblue4")
ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
ctrp_data$Drug_Gene_Lin <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol, "_", ctrp_data$group_general_lineage_name)
saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds", compress = "xz")

# GDSC
gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
gdsc <- merge(drug_meta, gdsc, by = "CID")
gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = g2p_genes)
gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Wildtype", gdsc_data$Mutation_Status_Nonsilent)
gdsc_data <- merge(gdsc_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
# gdsc_data <- merge(gdsc_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
gdsc_data <- merge(gdsc_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
gdsc_data$AUC_zscore <- (gdsc_data$AUC - mean(gdsc_data$AUC)) / sd(gdsc_data$AUC)
gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Wildtype", "paleturquoise3", "turquoise4")
gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
gdsc_data$Drug_Gene_Lin <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol, "_", gdsc_data$group_general_lineage_name)
saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds", compress = "xz")
```

@@

# Filter drug screen datasets for G2P drug-gene-lineage associations
ccle_data_g2p_dgl <- filter(ccle_data_ptmuts, Drug_Gene_Lin %in% g2p_druggenelins)
ccle_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
ctrp_data_g2p_dgl <- filter(ctrp_data_ptmuts, Drug_Gene_Lin %in% g2p_druggenelins)
ctrp_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
gdsc_data_g2p_dgl <- filter(gdsc_data_ptmuts, Drug_Gene_Lin %in% g2p_druggenelins)
gdsc_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))

@@

```{r, eval=FALSE}
ccle_signif_grid_lineage <- lapply(unique(ccle_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_grid, data_name = "ccle", grouping_var = "lineage")
names(ccle_signif_grid_lineage) <- unique(ccle_signif_grid_lineage$Drug)
ccle_signif_grid_lineage <- rbindlist(ccle_signif_grid_lineage, use.names = TRUE)
ccle_signif_grid_lineage <- ccle_signif_grid_lineage[order(ccle_signif_grid_lineage$p),]
saveRDS(ccle_signif_grid_lineage, "./data_munging/rds/ccle_signif_grid_lineage.rds")

ccle_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ccle_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
ccle_signif_g2p_lineage <- adj_signif(ccle_signif_g2p_lineage)
ccle_signif_g2p_lineage <- ccle_signif_g2p_lineage[order(ccle_signif_g2p_lineage$p),]
saveRDS(ccle_signif_g2p_lineage, "./data_munging/rds/ccle_signif_g2p_lineage.rds")
```

```{r}
ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
ccle_signif_grid_lineage <- readRDS("./data_munging/rds/ccle_signif_grid_lineage.rds")

knitr::kable(ccle_signif_g2p_lineage[, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

knitr::kable(ccle_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r, eval=FALSE}
ctrp_signif_grid_lineage <- lapply(unique(ctrp_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_grid, data_name = "ctrp", grouping_var = "lineage")
names(ctrp_signif_grid_lineage) <- unique(ctrp_signif_grid_lineage$Drug)
ctrp_signif_grid_lineage <- rbindlist(ctrp_signif_grid_lineage, use.names = TRUE)
ctrp_signif_grid_lineage <- ctrp_signif_grid_lineage[order(ctrp_signif_grid_lineage$p),]
saveRDS(ctrp_signif_grid_lineage, "./data_munging/rds/ctrp_signif_grid_lineage.rds")

ctrp_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ctrp_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
ctrp_signif_g2p_lineage <- adj_signif(ctrp_signif_g2p_lineage)
ctrp_signif_g2p_lineage <- ctrp_signif_g2p_lineage[order(ctrp_signif_g2p_lineage$p),]
saveRDS(ctrp_signif_g2p_lineage, "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
```

```{r}
ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
ctrp_signif_grid_lineage <- readRDS("./data_munging/rds/ctrp_signif_grid_lineage.rds")

knitr::kable(ctrp_signif_g2p_lineage[, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

knitr::kable(ctrp_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r, eval=FALSE}
gdsc_signif_grid_lineage <- lapply(unique(gdsc_data_g2p_grid$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_grid, data_name = "gdsc", grouping_var = "lineage")
names(gdsc_signif_grid_lineage) <- unique(gdsc_signif_grid_lineage$Drug)
gdsc_signif_grid_lineage <- rbindlist(gdsc_signif_grid_lineage, use.names = TRUE)
gdsc_signif_grid_lineage <- gdsc_signif_grid_lineage[order(gdsc_signif_grid_lineage$p),]
saveRDS(gdsc_signif_grid_lineage, "./data_munging/rds/gdsc_signif_grid_lineage.rds")

gdsc_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = gdsc_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
gdsc_signif_g2p_lineage <- adj_signif(gdsc_signif_g2p_lineage)
gdsc_signif_g2p_lineage <- gdsc_signif_g2p_lineage[order(gdsc_signif_g2p_lineage$p),]
saveRDS(gdsc_signif_g2p_lineage, "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
```

```{r}
gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
gdsc_signif_grid_lineage <- readRDS("./data_munging/rds/gdsc_signif_grid_lineage.rds")

knitr::kable(gdsc_signif_g2p_lineage[, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

knitr::kable(gdsc_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

## G2P evidence

@@

crispr_mut_heatmap_plot <- ggplot(data = crispr_signif_g2p_gene, aes(x = Hugo_Symbol, y = y_label)) +
  geom_tile(aes(fill = p)) +
  scale_fill_gradientn(colors = c("darkgreen", "honeydew", "white"), values = c(0, 0.05, 1), na.value = "darksalmon") +
  scale_x_discrete(drop = FALSE) +
  theme(axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
  labs(x = "Gene")
crispr_mut_heatmap_plot

@@

```{r fig.height=5, fig.width=12}
crispr_res_mut <- select(crispr_signif_g2p_gene, Hugo_Symbol, p)
crispr_res_mut$corr <- 0
crispr_res_mut$Metric <- "Mutation Status"
crispr_res_mut$p_log10 <- -log10(crispr_res_mut$p)

crispr_pearson_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                    summarize(p = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              corr = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Metric = "Gene Expression")
subset(crispr_pearson_res_GE, p < 0.05)
